\bf An Empirical Comparison of Parametric and Permutation Tests for Regression Analysis of Randomized Experiments

### 2018-03-21 ms/ms.tex

Table~\ref{tab:clinical_pvalues} shows the $p$-values for the four tests and the seven continuous study endpoints.
Overall, the results confirm our expectations based on visual comparison in Figure~\ref{fig:clinical_distr}:
one or more of the tests reject the null hypothesis that outcomes are the same between treatments for heartburn frequency, daily heartburn, and daily ``hrdq,''
but not for any of the other endpoints.
The $p$-values for the stratified, unadjusted permutation test have no consistent pattern: sometimes they are smaller than the $p$-values from the other tests and sometimes they are larger.

@@

\begin{table}\label{tab:clinical_distr}
\centering
\begin{tabular}{r|cc|cc}
  \hline
 & Mean A & SD A & Mean B & SD B \\ 
  \hline
daily\_heart & 0.59 & 0.46 & 0.75 & 0.52 \\ 
  daily\_regurg & 0.52 & 0.44 & 0.58 & 0.45 \\ 
  daily\_dysp & 0.56 & 0.51 & 0.55 & 0.49 \\ 
  daily\_hrdq & 1.11 & 0.84 & 1.33 & 0.86 \\ 
  heart\_freq & 2.48 & 2.10 & 3.51 & 2.76 \\ 
  regurg\_freq & 2.30 & 1.97 & 2.58 & 2.16 \\ 
  dysp\_freq & 2.49 & 2.48 & 2.36 & 2.25 \\ 
   \hline
\end{tabular}
\caption{Mean of each continuous outcome in groups A and B.} 
\end{table}

\begin{table}[]
\centering
\label{tab:clinical_pvalues}
\begin{tabular}{l|LLLL}
Endpoint      & ANCOVA & Stratified Permutation & LM Permutation & Freedman-Lane \\ \hline
heart\_freq   & 0.035                      & 0.003                                                                                & 0.070                                                                        & 0.074                                                                       \\
regurg\_freq  & 0.136                      & 0.157                                                                                & 0.231                                                                        & 0.221                                                                        \\
dysp\_freq    & 0.565                      & 0.925                                                                               & 0.592                                                                        & 0.579                                                                        \\
daily\_heart & 0.032                      & 0.010                                                                                & 0.062                                                                        & 0.069                                                                        \\
daily\_regur  & 0.142                      & 0.195                                                                                & 0.250                                                                        & 0.243                                                                        \\
daily\_hrdq   & 0.043                      & 0.033                                                                                & 0.086                                                                        & 0.088                                                                        \\
daily\_dysp   & 0.582                      & 0.803                                                                                & 0.686                                                                        & 0.699                                                                        \\
\hline
\end{tabular}
\caption{Comparison of p-values from four tests, for each continuous endpoint.} 
\end{table}

>>>>

Table~\ref{tab:clinical_pvalues} shows the $p$-values for the four tests and the seven continuous study endpoints.
Overall, the results confirm our expectations based on Table~\ref{tab:clinical_distr}:
one or more of the tests reject the null hypothesis that outcomes are the same between treatments for heartburn frequency, daily heartburn, and daily ``hrdq,''
but not for any of the other endpoints.
The $p$-values for the stratified, unadjusted permutation test have no consistent pattern: sometimes they are smaller than the $p$-values from the other tests and sometimes they are larger.

@@

\begin{table}
\centering
\begin{tabular}{r|cc|cc}
  \hline
 & Mean A & SD A & Mean B & SD B \\ 
  \hline
daily\_heart & 0.59 & 0.46 & 0.75 & 0.52 \\ 
  daily\_regurg & 0.52 & 0.44 & 0.58 & 0.45 \\ 
  daily\_dysp & 0.56 & 0.51 & 0.55 & 0.49 \\ 
  daily\_hrdq & 1.11 & 0.84 & 1.33 & 0.86 \\ 
  heart\_freq & 2.48 & 2.10 & 3.51 & 2.76 \\ 
  regurg\_freq & 2.30 & 1.97 & 2.58 & 2.16 \\ 
  dysp\_freq & 2.49 & 2.48 & 2.36 & 2.25 \\ 
   \hline
\end{tabular}
\caption{Mean of each continuous outcome in groups A and B.} 
\label{tab:clinical_distr}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{l|LLLL}
Endpoint      & ANCOVA & Stratified Permutation & LM Permutation & Freedman-Lane \\ \hline
heart\_freq   & 0.035                      & 0.003                                                                                & 0.070                                                                        & 0.074                                                                       \\
regurg\_freq  & 0.136                      & 0.157                                                                                & 0.231                                                                        & 0.221                                                                        \\
dysp\_freq    & 0.565                      & 0.925                                                                               & 0.592                                                                        & 0.579                                                                        \\
daily\_heart & 0.032                      & 0.010                                                                                & 0.062                                                                        & 0.069                                                                        \\
daily\_regur  & 0.142                      & 0.195                                                                                & 0.250                                                                        & 0.243                                                                        \\
daily\_hrdq   & 0.043                      & 0.033                                                                                & 0.086                                                                        & 0.088                                                                        \\
daily\_dysp   & 0.582                      & 0.803                                                                                & 0.686                                                                        & 0.699                                                                        \\
\hline
\end{tabular}
\caption{Comparison of p-values from four tests, for each continuous endpoint.} 
\label{tab:clinical_pvalues}
\end{table}
